### 2015-05-08 dicook/gender.Rmd
added the review that we need to address

@@

>>>>

qplot(name, mathgap, data=student2012.sub.summary.gap, size=I(5), color=msig) + 
  scale_y_continuous("Math Score Gap", limits=c(-80, 30), breaks=seq(-80, 30, 5), labels=c(seq(80, 0, -5), seq(5, 30, 5))) + 

@@

qplot(name, readgap, data=student2012.sub.summary.gap, size=I(5), color=rsig) + 
  scale_y_continuous("Reading Score Gap", limits=c(-80, 30), breaks=seq(-80, 30, 5), labels=c(seq(80, 0, -5), seq(5, 30, 5))) + 
